%!TEX TS-program = xelatex
\documentclass[11pt]{friggeri-cv}
%\addbibresource{bibliography.bib}

\usepackage{multicol}
\setlength{\columnsep}{2cm}
\begin{document}
\header{Pritish } {Patil} 
        {\href{mailto:iampritishpatil@gmail.com}{iampritishpatil@gmail.com}\quad  
    \href{mailto:ugpatil@ug.iisc.in}{ugpatil@ug.iisc.in}\quad{ +91-8861-557-553}
}




% In the aside, each new line forces a line break
%\begin{aside}
%  \section{current address}
%    Room number 9
%    N-Block Hostel
%    Indian Institute of Science
%    Bangalore 560012
%    India
%  \section{permanent address}
%  19, Dhavalgiri Society
%  Takali Road
%  Nashik 422011
%  India  
%  \section{email id}
%    \href{mailto:iampritishpatil@gmail.com}{iampritishpatil@gmail.com}
%    \href{mailto:ugpatil@ug.iisc.in}{ugpatil@ug.iisc.in}
%  \section{phone}
%  +91-8861-557-553
%  \section{languages}
%    English
%    Marathi
%    Hindi
%  \section{programming}
%    C
%    R
%    Python
%    Matlab
%    \LaTeX
%    shell/bash
%  \section{computer skills}
%  linux/unix
%\end{aside}

\section{interests}

Dynamical Systems in Biology, Modelling Biological Systems, Neuroscience, Ecology, Systems Biology, Theoretical Biology, Spatial Dynamics, Mathematical Biology, Astronomy, Numerical Methods, Algorithms, Scientific Computing


\section{education}

\begin{entrylist}
  \entryy
    {2012--2016}
    {Bachelor of Science}
    {Indian Institute of Science, Bangalore}
    {Biology Major with Mathematics Minor \hspace{2em}
     CGPA 6.7/8.0  (After 5 semesters)}
  \entryy
    {2012}
    {12th Grade}
    {KVN Naik College, Nashik}
    {Science Stream \hspace{2em} 
      79.83\%}
  \entryy
    {2010}
    {10th Grade}
    {JDC Bytco High School, Nashik}
    {Matriculation \hspace{2em}    
    86.16\%}

\end{entrylist}


\section{major achievements}
\begin{entrylist}
  \entryy
    {2012}
    {International Biology Olympiad}
    {Singapore, Singapore}
    {Silver Medal}
  \entryy
    {2011}
    {International Biology Olympiad}
    {Taipei, Taiwan}
    {Silver Medal}
  \entryy
    {2010}
    {International Astronomy Olympiad}
    {Crimea, Ukraine}
    {Silver Medal}



\end{entrylist}

\section{research experience}
\begin{entrylist}
  \entry
    {2014}
    {Finding network topologies which show adaptation response}
    {NCBS, Bangalore}
    {Guide : Dr. Sandeep Krishna, NCBS, Bangalore}
    {Modelled a general three node gene/protein network using a system of differential equations and simulated it. The aim was to find the topologies which show the adaptation response. Used variable step-size 4th order Runge-Kutta routine to solve the system of differential equations.}
\end{entrylist}
\begin{entrylist}

  \entry
    {2013}
    {Modelling of High Energy Cosmic Ray Spectrum}
    {HBCSE, Mumbai}
    {Guide : Prof. Mayank Vahia, TIFR, Mumbai}
    {Explored the effect of magnetic field on cosmic rays produced inside galaxies and proposed an explanation for the features seen in the cosmic ray spectrum. Tried to explain galactic X-Ray halos using these cosmic rays. 
    }
\end{entrylist}
\begin{entrylist}
    
  \entry
    {2013}
    {Lab techniques for isolation and purification of proteins}
    {IISc Bangalore}
    {
    Guide : Prof. V. Nagaraja, IISc, Bangalore}
    {Learned various lab techniques like Polyacrylamide Gel Electrophoresis, Ion-exchange Chromatography, Affinity and Immunoaffinity Chromatography, Metal Chelate Affinity Chromatography,  Size-exclusion Chromatography. General techniques in microbiology were also learned.
    }    
\end{entrylist}
\begin{entrylist}

  \entry
    {2012}
    {Constraining Dark Energy Parameters using Supernova-1a data}
    {IISER, Mohali}
    {Guide : Prof H.K. Jassal, IISER Mohali}
    {Understood standard cosmology,  obtained constraints on dark energy parameters of the standard model and evaluated different cosmological models by comparing with SN1A data(Union Supernova Project).     }
    
\end{entrylist}
    \begin{entrylist}


  \entry
    {2011}
    {A stacking analysis of radio properties of photometrically selected quasars}
    {NCRA, Pune}
    {
    Guide : Dr. Yogesh Wadadekar, NCRA, Pune}
    {Analysed the radio properties of 1 million quasars (all the known quasars at that time) found by SDSS photometrically. Correlated the optical data to radio data by doing statistics on radio image stacks of quasars.}
    \end{entrylist}
    \begin{entrylist}
  \entry
    {2010}
    {Effect of metallicity on the evolution of stellar populations}
    {NCRA, Pune}
    {
    Guide : Dr. Yogesh Wadadekar, NCRA, Pune}
    {Studied the effects of changes in metallicity of a nebula upon the evolution of clusters of stars within it. 
    }

    \end{entrylist}
\begin{entrylist}
  \entry
    {2009}
    {Study of Irregularities in the Spiral Structure of M101}
    {HBCSE, Mumbai}
    {
    Guide : Prof. Mayank Vahia, TIFR, Mumbai}
    {Analysed the spiral structure of M101 Pinwheel galaxy, examined the irregularities  and proposed explanations for them. 
    }    
\end{entrylist}

\section{course projects}


\begin{entrylist}
\entry
    {2014}
    {Spatial Dynamics of Sympatric Speciation (Ongoing)}
    {Theoretical and Mathematical Ecology}
    {
    Prof. Vishwesha Guttal, IISc Bangalore}
    {Studied spatial dynamics of sympatric speciation due to disruptive selection. 
    }    
\end{entrylist}



\begin{entrylist}
\entry
    {2014}
    {Leeches:
Animal movements and random walks}
    {Experiment in Ecology}
    {
    Dr. Farah Ishtiaq, IISc Bangalore}
    {Explored how the leeches could be locating their prey in absence of stimulus. Found that the leeches perform a correlated random walk, which emulate a Levy random walk.
    }    
\end{entrylist}

\begin{entrylist}
  \entry
    {2014}
    {Comparing Weiner chaos decomposition and Monte Carlo methods for solving stochastic differential equations.}
    {Introduction to Scientific Computing}
    {
    Prof. S. Raha, IISc Bangalore}
    {Used Weiner Chaos Decomposition and Monte Carlo method to find the solutions of a system of stochastic differential equations numerically. Compared the accuracy  of and the time taken by these methods. 
    }    
\end{entrylist}
\begin{entrylist}
\entry
    {2014}
    {Sexual Selection with a Two Locus Model}
    {Theoretical and Mathematical Ecology}
    {
    Prof. Vishwesha Guttal, IISc Bangalore}
    {Modelled the effects of sexual selection on two loci in haploid and diploid systems analytically, and in more complex cases numerically. Studied various equilibria of the system and determined their stability. Analysed the dynamics of invasion of one genotype by another. 
    }    
\end{entrylist}






\section{programming and computers}
Proficient in C, R, Python,
    Matlab,
    \LaTeX,
    shell/bash and
    linux.



\section{other notable achievements}

\begin{entrylist}
  \entryy
    {2011}
    {Selected as a member of Indian team for International Earth Science Olympiad}
    {Modena, Italy}
    {One of top 4 from India to get selected.}
\end{entrylist}


\begin{entrylist}
  \entryy
    {2011 -- 2014}
    {Recipient of KVPY (Kishore Vaigyanik Protsahan Yojana) Scholarship}{}
    {Awarded to the top 200 science students from India each year.}

\end{entrylist}


\begin{entrylist}
  \entryy
    {2009 -- 2011}
    {Recipient of NTSE (National Talent Search Exam) Scholarship}{}
    {Awarded to the top 1000 students from India each year.}
\end{entrylist}


\begin{entrylist}
  \entryy
    {2013}
    {Regionals of ACM International Collegiate Programming Contest}
    {Amrita University Coimbatore}
    {One of the top 389 teams selected from across the country}
\end{entrylist}


\begin{entrylist}
  \entryy
    {2013}
    {Won MIMAMSA, a national inter-college science quiz}
    {IISER, Pune}
    {Qualified for the final quiz from amongst more than 100 teams and WON the 14 hours long quiz.}
\end{entrylist}







\begin{multicols}{2}[]

\setlength\columnsep{0em}

\begin{minipage}{1.1\columnwidth}
\section{relevant courses (grad level)}


\subsection{biology}

\begin{itemize}

\item Topics in Systems Neuroscience
\item Theoretical and Computational Neuroscience
\item Theoretical and Mathematical Ecology
\item Spatial Dynamics in Biology
\item Cellular Neurophysiology
\item Fundamentals of Systems and Cognitive Neuroscience
\item Fundamentals of Molecular and Cellular Neuroscience
\end{itemize}


\subsection{mathematics}
\begin{itemize}
\item Probability Theory
\item Measure theory
\item Linear Algebra
\item Real Analysis
\end{itemize}

\subsection{engineering}
\begin{itemize}
\item Information Theory
\end{itemize}





\end{minipage}

\begin{minipage}{1.1\columnwidth}



\section{relevant courses (undergrad level)}

\subsection{biology}
\begin{itemize}
\item Developmental Biology
\item Introductory Structural Biology
\item General Biochemistry
\item Introductory Physiology
\item Laboratory courses in Biology

\begin{itemize}
\item Biochemistry and Physiology
\item Microbiology and Ecology
\item Molecular Biophysics
\item Neurobiology
\item 3 semesters of introductory lab courses
\end{itemize}

\end{itemize}


\subsection{mathematics}
\begin{itemize}
\item Multivariable Calculus and Complex Variables
\item Elementary Algebra and Number Theory
\item Probability and Statistics
\end{itemize}



\subsection{engineering}
\begin{itemize}
\item Introduction to Scientific Computing
\item Algorithms and Programming
\item Introduction to Electrical and Electronics Engineering
\end{itemize}


\end{minipage}

\end{multicols}





\section{camps attended}

\begin{entrylist}
  \entryy
    {2014}
    {Physics of Life, NCBS-Simons Annual Monsoon School}
    {NCBS, Bangalore}
    {Topics included: biophysics and soft-matter physics, ranging from aspects molecules to those of cells and tissues; information processing and decision making, at the level of cells or of the brain; stochastic processes in molecules or populations; dynamical systems models of genetic networks or biomechanical systems.}
    
\end{entrylist}


\begin{entrylist}
  \entryy
    {2012 2013}
    {NIUS Astronomy Nurture Camp}
    {HBCSE Mumbai}
    {Worked on various astronomical projects listed above.}
\end{entrylist}


\begin{entrylist}
  \entryy
    {2011, 2012}
    {Vijyoshi Camp}
    {IISc, Bangalore}
    {Similar to Lindau Meet with Noble Laureates for students. For top \approx 600 science students across India }
    
\end{entrylist}









\section{extracurricular activities}

\begin{entrylist}
  \entryy
    {2014-2015}
    {Programming Events Manager for Pravega, the annual college festival}
    {IISc, Bangalore}
    {Reverse coding: given the executable, write the source code. Online programming contest: a standard programming contest. Connect the dots: a programming treasure hunt, which requires you to solve programming questions to get to the next question}
\end{entrylist}

\begin{entrylist}
  \entryy
    {2013--2014}
    {Convener and founder of Scipher}
    {Bangalore}
    {Scipher is a mock test for the KVPY scholarship exam. We set a model question paper and conducted the model exam across various states in India. 3,500 students took the mock exam Coordinated with ~30 people for setting and designing question paper. Co-ordinated with ~70 people for conduction and supervision of the examination.}
\end{entrylist}







%\section{experience}
%
%\begin{entrylist}
%  \entry
%    {02–07 2009}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Visualization of complex networks.}}
%  \entry
%    {06–08 2008}
%    {ISCPIF/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
%  \entry
%    {06–08 2007}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Kernels in real world networks.}}
%  \entry
%    {07–08 2005}
%    {\href{http://www.kelkoo.com}{Kelkoo.com}}
%    {Summer job.}
%    {\emph{Creation of a keyword generator for Google Adwords.}}
%  \entry
%    {07–08 2004}
%    {\href{http://www.monsieurprix.com}{MonsieurPrix.com}}
%    {Summer job.}
%    {\emph{Development of an e-commerce product indexation spider.}}
%\end{entrylist}
%
%\section{applications}
%
%\begin{entrylist}
%  \entry
%    {2012}
%    {Who did I forget ?}
%    {\href{http://whodidiforget.com}{whodidiforget.com}}
%    {Guest list recommendation for Facebook events based on friends already attending the event.}
%  \entry
%    {2011}
%    {Fellows}
%    {\href{http://fellows-exp.com}{fellows-exp.com}}
%    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%  \entry
%    {2008}
%    {Happy Flu}
%    {\href{http://happyflu.com}{happyflu.com}}
%    {Experiment aimed to measure viral spreading of content across the blogosphere.}
%\end{entrylist}

%\section{publications}
%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}


\textit{ You can email me for the longer, more detailed version of my CV.}

\end{document}
