%!TEX TS-program = xelatex

\documentclass[11pt,print]{friggeri-cv}%
%\addbibresource{bibliography.bib}


\usepackage{enumitem}

\usepackage{multicol}

\usepackage{layouts}




\setlist[itemize]{leftmargin=*}

\setlength{\columnsep}{2cm}
\begin{document}
\header{Pritish } {Patil} 
        {\href{mailto:iampritishpatil@gmail.com}{iampritishpatil@gmail.com}\quad  
    \href{mailto:pritish.patil@weizmann.ac.il}{pritish.patil@weizmann.ac.il}
}




\section{education}

\begin{entrylist}
  \entryyy
    {2016--pres}
    {Master of Science {\normalfont Brain Sciences }  }
    {Weizmann Institute of Science, Rehovot}

  \entryyy
    {2012--2016}
    {Bachelor of Science {\normalfont Biology Major with Mathematics Minor }  }
    {Indian Institute of Science, Bangalore}
%  \entryyy
%    {2012}
%    {12th Grade {\normalfont Science Stream} }
%  {KVN Naik College, Nashik}
%  \entryyy
%    {2010}
%    {10th Grade     {\normalfont Matriculation}}
%    {JDC Bytco High School, Nashik}
\end{entrylist}


\section{major achievements}
\begin{entrylist}
  \entryyy
    {2012}
    { {\normalfont Silver Medal at }International Biology Olympiad     }
    {Singapore, Singapore}
    
  \entryyy
    {2011}
    {  {\normalfont Silver Medal at }International Biology Olympiad}
    {Taipei, Taiwan}
    
  \entryyy
    {2010}
    { {\normalfont Silver Medal at }International Astronomy Olympiad }
    {Crimea, Ukraine}



\end{entrylist}

\section{research experience}

\begin{entrylist}
  \entry
    {2015 -- 2016}
    {Bachelors thesis: Making a realistic model CA1 Pyramidal Neuron in MOOSE}
    {NCBS, Bangalore}
    {Guide : Prof. Upinder S Bhalla, NCBS, Bangalore}
    {Coming up with a distrubution ion channels for the CA1 Pyramidal neurons which has realistic behavior for different morphologies. All coding in MOOSE}
\end{entrylist}
\begin{entrylist}
  \entry
    {2014}
    {Finding network topologies which show adaptation response}
    {NCBS, Bangalore}
    {Guide : Dr. Sandeep Krishna, NCBS, Bangalore}
    {Modelled a general three node gene/protein network using a system of differential equations and simulated it. The aim was to find the topologies which show the adaptation response.}
\end{entrylist}
\begin{entrylist}

  \entry
    {2013}
    {Modelling of High Energy Cosmic Ray Spectrum}
    {HBCSE, Mumbai}
    {Guide : Prof. Mayank Vahia, TIFR, Mumbai}
    {Explored the effect of magnetic field on cosmic rays produced inside galaxies and proposed an explanation the features of cosmic ray spectrum. Tried to explain galactic X-Ray halos using these cosmic rays.}
\end{entrylist}
\begin{entrylist}
    
  \entry
    {2013}
    {Lab techniques for isolation and purification of proteins}
    {IISc Bangalore}
    {
    Guide : Prof. V. Nagaraja, IISc, Bangalore}
    {Learned various lab techniques like PAGE, various types of chromatography and Genenreal techniques in microbiology.}    
\end{entrylist}
\begin{entrylist}

  \entry
    {2012}
    {Constraining Dark Energy Parameters using Supernova-1a data}
    {IISER, Mohali}
    {Guide : Prof H.K. Jassal, IISER Mohali}
    {Understood standard cosmology,  obtained constraints on dark energy parameters of the standard model and evaluated different cosmological models by comparing with SN1A data(Union Supernova Project).
    }
    
\end{entrylist}
\begin{entrylist}


  \entry
    {2012}
    {Karyotyping for screening of chromosomal abnormalities}
    {Genetic Health \& Research Centre, Nasik}
    {
    Guide : Dr. Dnyandeo Chopade, Genetic Health \& Research Centre, Nasik}
    {
    Mastered the basics of Karyotyping. Learned to make karyotypes from blood and from chorionic villi.  Apprenticed for  detection of defects in chromosomes in the karyotypes.
    }
    \end{entrylist}
    \begin{entrylist}


  \entry
    {2011}
    {A stacking analysis of radio properties of photometrically selected quasars}
    {NCRA, Pune}
    {
    Guide : Dr. Yogesh Wadadekar, NCRA, Pune}
    {Analysed the radio properties of 1 million quasars found by SDSS photometrically. Correlated the optical data to radio data and did statistics on radio image stacks of quasars.
    }
    \end{entrylist}
    \begin{entrylist}
  \entry
    {2010}
    {Effect of metallicity on the evolution of stellar populations}
    {NCRA, Pune}
    {
    Guide : Dr. Yogesh Wadadekar, NCRA, Pune}
    {Studied the effects of changes in metallicity of a nebula upon the evolution of clusters of stars within it.
    }

    \end{entrylist}
\begin{entrylist}
  \entry
    {2009}
    {Study of Irregularities in the Spiral Structure of M101}
    {HBCSE, Mumbai}
    {
    Guide : Prof. Mayank Vahia, TIFR, Mumbai}
    {Analysed the spiral structure of M101 Pinwheel galaxy, examined the irregularities  and proposed explanations for them. 
    }    
\end{entrylist}

\section{course projects}


\begin{entrylist}
\entry
    {2015}
    {Analysis of Dendritic transmission}
    {Theoretical and Computational Neuroscience}
    {
    Prof. Rishikesh Narayanan and Prof. SP Arun, IISc Bangalore}
    {Using a realistic detailed neuronal model, studied dendritic transmission and computation. Using only poisson input and corresponding output spike trains, calculated time for dendritic transmission, and after correcting for this delay, analyzed synaptic processing using K-means clustering and mutual information.}    
\end{entrylist}
\begin{entrylist}
\entry
    {2014}
    {Spatial Dynamics of Sympatric Speciation}
    {Theoretical and Mathematical Ecology}
    {
    Prof. Vishwesha Guttal, IISc Bangalore}
    {Studied spatial dynamics of sympatric speciation due to disruptive selection. Reproduced some of the results in ``Speciation along environmental gradients'' by Michael Doebeli and Ulf Dieckmann.
    }    
\end{entrylist}
\begin{entrylist}
\entry
    {2014}
    {Leeches:
Animal movements and random walks}
    {Experiment in Ecology}
    {
    Dr. Farah Ishtiaq, IISc Bangalore}
    {Explored how the leeches could be locating their prey in absence of stimulus. Found that the leeches perform a correlated random walk, which emulates a Levy random walk.
    }    
\end{entrylist}
\begin{entrylist}
  \entry
    {2014}
    {Comparing Weiner chaos decomposition and Monte Carlo methods for solving stochastic differential equations.}
    {Introduction to Scientific Computing}
    {
    Prof. S. Raha, IISc Bangalore}
    {Used Weiner Chaos Decomposition and Monte Carlo method to find the solutions of a system of stochastic differential equations numerically. Compared the accuracy  of and the time taken by these methods.
    }    
\end{entrylist}
\begin{entrylist}
\entry
    {2014}
    {Sexual Selection with a Two Locus Model}
    {Theoretical and Mathematical Ecology}
    {
    Prof. Vishwesha Guttal, IISc Bangalore}
    {Modelled the effects of sexual selection on two loci in haploid and diploid systems analytically and other complex cases. Studied the equilibria of the system and determined their stability. Analysed the dynamics of invasion of one genotype by another. 
    }    
\end{entrylist}

\section{programming and computers}


\begin{multicols}{2}[]

\begin{minipage}{1.1\columnwidth}

\subsection{common programming}
C,
 Python,
  R, 
    MATLAB,
{    \lotsoftextfont \LaTeX},
    shell/bash,
    linux.

\end{minipage}

\hspace{-1em}
\begin{minipage}{1.05\columnwidth}
    

\subsection{neuroscience related}
MOOSE, NEURON, BRIAN 

\end{minipage}

\end{multicols}


\section{teaching}

\begin{entrylist}
  \entry
    {2015}
    {Computational Approaches to Memory and Plasticity }
    {NCBS, Bangalore}
    {16-day summer school on the theory and simulation of learning, memory and plasticity in the brain.}
    {I taught tutorials in 1. Machine Learning for neural data analysis 2. Rate models of neurons 3. Building a multiscale model from scratch. I was also involved in designing and guiding with the miniprojects in the course.  }
\end{entrylist}



\pagebreak

\section{camps and workshops attended}

\begin{entrylist}
  \entryy
    {2015}
    {Computational Approaches to Memory and Plasticity }
    {NCBS, Bangalore}
    {16-day summer school on the theory and simulation of learning, memory and plasticity in the brain.}    
\end{entrylist}
\begin{entrylist}
  \entryy
    {2014}
    {Physics of Life, NCBS-Simons Annual Monsoon School}
    {NCBS, Bangalore}
    {Topics included: biophysics and soft-matter physics; information processing and decision making; stochastic processes in molecules or populations; dynamical systems models of genetic networks or biomechanical systems.}    
\end{entrylist}
\begin{entrylist}
  \entryy
    {2011, 2012}
    {Vijyoshi Camp}
    {IISc, Bangalore}
    {Similar to Lindau Meet with Noble Laureates for students. For top \approx 600 science students across India }
\end{entrylist}

\section{other notable achievements}

\begin{entrylist}
  \entryy
    {2017}
    {Prize of Excellence}
    {By Ekard Research School of Biological Science}
    {In recognition of achievements in undergraduate studies}
\end{entrylist}
\begin{entrylist}
  \entryy
    {2011}
    {Selected as a member of Indian team for International Earth Science Olympiad}
    {Modena, Italy}
    {One of top 4 from India to get selected.}
\end{entrylist}
\begin{entrylist}
  \entryy
    {2011 -- 2016}
    {Recipient of KVPY (Kishore Vaigyanik Protsahan Yojana) Scholarship}{}
    {Awarded to the top 200 science students from India each year.}

\end{entrylist}
\begin{entrylist}
  \entryy
    {2009 -- 2011}
    {Recipient of NTSE (National Talent Search Exam) Scholarship}{}
    {Awarded to the top 1000 students from India each year.}
\end{entrylist}


\section{relevant courses [grad level]}

\begin{multicols}{2}[]

\begin{minipage}{1.1\columnwidth}

\subsection{neuroscience}
\begin{itemize}
\item Theoretical Models Of Memory: Long-Term, Short-Term, Episodic And More
\item Classic Papers In The Neuroscience
\item Seminar On Data Analysis For Neuroscience
\item Systems Neuroscience Reading Seminar
\item Topics in Systems Neuroscience
\item Theoretical and Computational Neuroscience
\item Cellular Neurophysiology
\item Fundamentals of Systems and Cognitive Neuroscience
\item Fundamentals of Molecular and Cellular Neuroscience
\item Introduction To Neuroscience: Systems Neuroscience
\item Introduction To Neuroscience: Molecular Neuroscience - Genes To Behavior
\item Neuroanatomy	
\end{itemize}


\end{minipage}

\hspace{-1em}
\begin{minipage}{1.05\columnwidth}

\subsection{mathematics}
\begin{itemize}
\item Stochastic Processes {\small[martingales and brownian motion]}
\item Probability Theory {\small[measure theoretic]}
\item Measure theory
\item Algebra
\item Topology
\item Linear Algebra
\item Real Analysis
\end{itemize}

\subsection{others}
\begin{itemize}
\item Theoretical and Mathematical Ecology
\item Spatial Dynamics in Biology
\item Information Theory
\item Pattern Recognition and Neural Networks
\item Non Equilibrium, Information And Control In Biology
\end{itemize}


\end{minipage}

\end{multicols}

\section{relevant courses [undergrad level]}

\begin{itemize}




\item Biology:
Introductory Structural Biology,
General Biochemistry,
Introductory Physiology,
Developmental Biology,



\item Mathematics:
Multivariable Calculus and Complex Variables , 
Elementary Algebra and Number Theory



\item Engineering:
Introduction to Scientific Computing,
Algorithms and Programming,
Introduction to Electrical and Electronics Engineering,
Introduction to Material Sciences,
Introduction to Environmental Sciences,


\item Laboratory courses:
 Experiments in Biochemistry and Physiology,
 Experiments in Microbiology and Ecology,
 Experiments in Molecular Biophysics,
 Experiments in Neurobiology,

\item  Introductory courses : 
 Physics {\small[3 courses]},
 Chemistry {\small[3 courses]},
 Mathematics {\small[3 courses]},
 Biology {\small[3 courses]},



\end{itemize}



%\section{experience}
%
%\begin{entrylist}
%  \entry
%    {02–07 2009}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Visualization of complex networks.}}
%  \entry
%    {06–08 2008}
%    {ISCPIF/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
%  \entry
%    {06–08 2007}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Kernels in real world networks.}}
%  \entry
%    {07–08 2005}
%    {\href{http://www.kelkoo.com}{Kelkoo.com}}
%    {Summer job.}
%    {\emph{Creation of a keyword generator for Google Adwords.}}
%  \entry
%    {07–08 2004}
%    {\href{http://www.monsieurprix.com}{MonsieurPrix.com}}
%    {Summer job.}
%    {\emph{Development of an e-commerce product indexation spider.}}
%\end{entrylist}
%
%\section{applications}
%
%\begin{entrylist}
%  \entry
%    {2012}
%    {Who did I forget ?}
%    {\href{http://whodidiforget.com}{whodidiforget.com}}
%    {Guest list recommendation for Facebook events based on friends already attending the event.}
%  \entry
%    {2011}
%    {Fellows}
%    {\href{http://fellows-exp.com}{fellows-exp.com}}
%    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%  \entry
%    {2008}
%    {Happy Flu}
%    {\href{http://happyflu.com}{happyflu.com}}
%    {Experiment aimed to measure viral spreading of content across the blogosphere.}
%\end{entrylist}

%\section{publications}
%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
